Running simulations of MultipleContactNeutralMigrat.nlogo

### 2022-11-14 RunSims.Rmd
Add new Rmd with simulation runs

---
title: "Single large or Several Small SLOSS "
author: "Leonardo A. Saravia"
date: "9/3/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

needed_packages <- c(
    "tidyverse"
  , "lubridate"
  , "nlrx")

@@

#### make changes
# Unix default NetLogo installation path (adjust to your needs!):
netlogopath <- file.path("/home/leonardo/NetLogo")
simfolder <- "/home/leonardo/Dropbox/Projects/ariadnaNL"
modelpath <- file.path(simfolder, "ariadnaNL.nlogo")
outpath <- file.path(simfolder,"Simulations")

@@

nl <- nl(nlversion = "6.1.1",
         nlpath = netlogopath,
         modelpath = modelpath,
         jvmmem = 2048)

@@

## Simulaciones para ajuste usando Latin Hypercubic Sampling

* Incursion by common, generalist species. 
* Minimun patch size selective extinction and nestedness
* Time since patch creation, accumulation of species losses
* Habitat heterogeneity environmental clumping patchy species distribution
* Dominance of colonization/inmigration
* Population variability spreading the risk

@@

```{r SLOSS_lambda4_simulations}
require(tidyverse)

# Neutral communities 
#
mdl <- read_netlogo_simul("Simulations/MultipleContactNeutralMigrat_NoSelection_pf06_hpf3-59_dd1-3.csv")
sloss_sim <- mdl

require(plotly)
plot_ly(data=mdl1, x=~birds_dispersal_distance, y=~habitat_patch_size, z=~calc_number_of_species, type="scatter3d", mode="markers", color=~calc_number_of_species, marker = list(size = 1))

@@

```{r SLOSS_lambda4_simulations}
require(tidyverse)

@@

* 100x100 world

```{r SLOSS_notfrag_simulations}
require(tidyverse)

@@

```{r SLOSS_combined_plots}

@@

```{r SLOSS_combined_plots}
require(tidyverse)

>>>>

---
title: "Running simulations of MultipleContactNeutralMigrat.nlogo"
author: "Leonardo A. Saravia"
date: "8/11/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

needed_packages <- c(
    "tidyverse"
  , "lubridate"
  , "future"
  , "tictoc"
  , "nlrx")

@@

#
# Where the NetLogo model is
# Setup for nlrx 
#
if( Sys.info()['nodename'] =="ls-pro") {
  simfolder <- "/home/leonardo/Dropbox/Projects/DynamicForestExtinction"

} else if(Sys.info()['nodename'] =="biologia2018") {                     # Server UNGS
  simfolder <- "/home/leonardo/Dropbox/Projects/DynamicForestExtinction"

}

# Unix default NetLogo installation path (adjust to your needs!):
#
netlogopath <- file.path("/home/leonardo/NetLogo")
modelpath <- file.path(simfolder, "MultipleContactNeutralMigrat.nlogo")
outpath <- file.path(simfolder,"Simulations")

@@

nl <- nl(nlversion = "6.2",
         nlpath = netlogopath,
         modelpath = modelpath,
         jvmmem = 2048)

@@

@@

```{r SLOSS_lambda4_simulations_lambda4,echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=TRUE}

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
#
nl@experiment <- experiment(expname="NoSelection_pf06_hps3-61_dd1-3",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "birth-rate-birds" = 4,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.001,
                                             "Video" = "false",
                                             "prob-frag" =  0.6,
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"NoSelection\"",
                                             "replacement-rate" = 0.0
                                             ))

#
# Run 10 times this do not set the run variable for output 
#
# nseeds * number_of_parameters / split = 10 * 300 / 4 - total number of jobs = nseeds * split = 10*4
#

nl@simdesign <- simdesign_ff(nl=nl,
                               nseeds=10)

# run in Paralell 
#
plan(multisession)
tic()
results <- run_nl_all(nl,split = 4)
#results <- run_nl_all(nl,split = 4)
toc()
plan(sequential)
names(results)

#
# Write the output 
#
setsim(nl, "simoutput") <- results 
write_simoutput(nl)
```

```{r readSimulations, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
# Read previous simulations
#
if( file.exists("Simulations/sloss_sim_ff.rds")) {

  sloss_sim <- readRDS("Simulations/sloss_sim_ff.rds")

} else {
  sloss_sim <- tibble()
}

# Read netlogo simulations and 
# Convert the list of mean_free_path to degraded_mfp and non_degraded_mfp
#
mdl <- read_netlogo_simul(file.path(outpath,"NoSelection_pf06_hps3-61_dd1-3_ff.csv"),skip=0) %>% 
  mutate(mean_free_path=str_sub(mean_free_path,2,-2)) %>% 
  separate(mean_free_path, c("non_degraded_mfp","degraded_mfp"), sep=" ",convert=TRUE)

## Old code to plot

# Neutral communities 
#
names(mdl)
#
# Plot for neutral communities 
#
mdl1 <- mdl %>% group_by(birds_dispersal_distance, habitat_patch_size) %>% summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )

# require(plotly)
# plot_ly(data=mdl1, x=~birds_dispersal_distance, y=~habitat_patch_size, z=~calc_number_of_species, type="scatter3d", mode="markers", color=~calc_number_of_species, marker = list(size = 1))

@@

```{r SLOSS_lambda4_simulations_lambda2,echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
require(tidyverse)

@@

```{r SLOSS_notfrag_simulations, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
require(tidyverse)

@@

```{r SLOSS_combined_plots, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

@@

```{r SLOSS_combined_plots1, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
require(tidyverse)
